Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-11-18 paper.qmd
Updated Figure 5

@@

trimesh_two_curvy_removed1_umap_with_data <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
             alpha = 0.5,
             size = 0.5) +
  coord_equal() +
  # theme(
  #   aspect.ratio = 1
  #   ) +
  interior_annotation("b", sc_ltr_pos)
```

@@

nldr_two_curvy_original + 
  trimesh_two_curvy_removed1_umap_with_data +
  two_curvy_proj_umap_first_model1 +
  two_curvy_proj_umap_all_model1 +
  plot_layout(ncol = 2, heights = c(1, 2))
```

>>>>

nldr_two_curvy2 <- umap_two_curvy_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#636363", size = 0.5) +
  interior_annotation("a", sc_ltr_pos)

@@

trimesh_two_curvy_removed1_umap_with_data <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
             alpha = 0.5,
             size = 0.5) +
  #coord_equal() +
  # theme(
  #   aspect.ratio = 1
  #   ) +
  interior_annotation("b", sc_ltr_pos)
```

@@

nldr_two_curvy2 + 
  trimesh_two_curvy_removed1_umap_with_data +
  two_curvy_proj_umap_first_model1 +
  two_curvy_proj_umap_all_model1 +
  plot_layout(ncol = 2, heights = c(1, 2))
```
